The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-06 writing/draft3/draft8.tex
copying the literature. Most of it had somewhiat dissappeared. a
also working

Following the procedure described above, we calculated a number of previously used characteristics of precipitation and temperature. Only some of them were found significant predictors of maize yield. These include: Total seasonal precipitation and 
\subsection{Statistical approach}

@@

\item relative importance of the individual variables and its measure
%\item Possibly estimate simple regressions with the same explanatory variables as the preferred mixed effects specification. This would give us an approximation of $R^2$ which could be used to compare our models.

>>>>

Following the procedure described above, we calculated a number of previously used characteristics of precipitation and temperature. Only some of them were found significant predictors of maize yield. These include: Total seasonal precipitation and its squared values, average seasonal temperature, coefficient of variation of seasonal precipitation, standard deviation of average seasonal temperature,  maximum length of dry spell in number of days, the number of dry spell lasting for four days or more

We did not include squared values of the average seasonal temperature as it was not significant.
\subsection{Statistical approach}

@@

\item relative importance of the individual variables and its measures
%\item Possibly estimate simple regressions with the same explanatory variables as the preferred mixed effects specification. This would give us an approximation of $R^2$ which could be used to compare our models.
